---
title: "Figure6_Analysis"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 3
    highlight: tango
---

# Setup

## Dependencies

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(scales)
library(patchwork)
library(cowplot)

library(tidyverse)
library(broom)
library(lme4)
library(ggExtra)
library(ggthemes)
library(scales)
library(Hmisc)
library(Metrics)
library(plotrix)
library(pheatmap) 
library(RColorBrewer)
library(networkD3) 

```

## Global configuration 

```{r}
global_text_size = 22
custom_theme = theme_classic() + theme(text = element_text(size=global_text_size))
theme_set(custom_theme)

```

# Analysis & plotting


## Main figure

### Common plot utilities

The neural-activity plots and stop-raster plots share some common features (same x axis, track shading), so we define them here to avoid repetition.


```{r}

common_geom_track_shading <- list(
  # Reward zone shading
  geom_rect(fill = rz_colour, xmin = FIRST_BLACKBOX_END + RZ_START, xmax = FIRST_BLACKBOX_END + RZ_END, ymin = -Inf, ymax = Inf),
  # Beginning blackbox shading
  geom_rect(fill = blackbox_colour, xmin = 0, xmax = FIRST_BLACKBOX_END, ymin = -Inf, ymax = Inf),
  # Ending blackbox shading
  geom_rect(fill = blackbox_colour, xmin = SECOND_BLACKBOX_START, xmax = TRACK_LENGTH, ymin = -Inf, ymax = Inf))

common_geom_track_x_axis <- list(
  scale_x_continuous(breaks = c(0, (RZ_START + RZ_END) / 2, TRACK_LENGTH), expand = c(0, 1)),   # (expand to make move the black box close to y axis)
  expand_limits(x = c(0, TRACK_LENGTH)))
```


### Subfig: Training results

```{r}
timestep_limit = 30e6

p_training <- training_progress %>% 
  ggplot(aes(timestep, reward)) +
  geom_line() + 
  scale_x_continuous(labels = unit_format(unit = "M", scale = 1e-6), limits = c(0, timestep_limit)) + 
  labs(x = 'Training steps', y = 'Reward')


p_training
```

### Subfigs: Behavioural (stop) raster plots for trained, untrained, probe

```{r}
rz_colour <- rgb(205, 227, 207, maxColorValue = 255)
blackbox_colour <- rgb(208, 208, 208, maxColorValue = 255)

n_trials_to_plot = 50


plot_behaviour <- function(data, is_probe) {
  data <- data %>% filter(global_trial_number <= n_trials_to_plot)
  
  # Hack to make all stops unrewarded for probe trials. 
  # (In the simulations, -1 is for unnecessary stops, and 100 is for rewarded stops)
  if (is_probe) {
    data$reward <- -1
  }
  
  data <- data %>% filter(action == 0, neuron_id == 1)
  data %>% 
    ggplot(aes(location, global_trial_number)) +
    common_geom_track_shading +
    geom_point(data=subset(data, reward == -1), aes(), alpha=0.7) +
    # Rewarded stops
    geom_point(data=subset(data, reward == 100), aes(), alpha=1, colour='red', shape=-9658, size=3) +
    scale_colour_manual(values = c('black', 'red')) +
    common_geom_track_x_axis +
    theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()) +  # hide x axis
    labs(x = 'Location', y = 'Trial') 
}


p_untrained_behaviour <- plot_behaviour(untrained_behaviour, is_probe = FALSE)
p_trained_behaviour <- plot_behaviour(trained_behaviour, is_probe = FALSE)
p_probe_behaviour <- plot_behaviour(probe_behaviour, is_probe = TRUE)

# Plot them for rmd
p_untrained_behaviour
p_trained_behaviour
p_probe_behaviour

```

### Subfig: neuron activations


```{r}

n_trials_to_plot <- 50

plot_activations <- function(data, labels) {
  
  lm_results <- function (row) {
    return("placeholder")
  }
  
  data %>% 
    group_by(neuron_id, location) %>%
    summarise(mean_neuron_activity = mean(neuron_activity), sd_neuron_activity = sd(neuron_activity)) %>%
    left_join(neuron_labels) %>%
    ggplot(aes(location, mean_neuron_activity)) +
    common_geom_track_shading +
    geom_ribbon(aes(ymin = mean_neuron_activity - sd_neuron_activity, ymax = mean_neuron_activity + sd_neuron_activity), fill = "grey70") +
    geom_line() +
    common_geom_track_x_axis +
    facet_wrap(. ~  label, ncol = 2, strip.position = 'top', scales = 'free_y') +
    theme(strip.background = element_blank()) +
    theme(strip.text=element_text(size = global_text_size-2, margin=margin(l = 50, b = 5, unit='pt'))) +
    theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank()) +  # Hide the x axis
    labs(x = 'Location', y = 'Activation')  +
    scale_y_continuous(breaks = pretty_breaks(), expand = c(0, 0), limits = c(0, NA))
}


p_activations <- 
  plot_activations(trained_behaviour %>% filter(global_trial_number <= n_trials_to_plot, neuron_id %in% neuron_ids), neuron_labels)


p_activations

```

### Subfigs: r^2 shuffled and real


```{r}
level_order <- c("Negative", "Positive", "Unclassified")

p_r2_real <- ggplot(data=spatial_firing, aes(x= asr_b_o_rewarded_fit_r.squared, fill=factor(unlist(lm_group_b), level = level_order))) +
  coord_cartesian(xlim = c(0,1)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
  ylab("Proportion") +
  xlab("\nrsquared") +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  scale_y_continuous(breaks=c(0.00, 0.06)) +
  theme_classic() +
  theme(legend.position = c(0.6, 0.7), legend.title = element_blank(), axis.title.x = element_blank())
    

p_r2_real 

p_r2_shuffled <- ggplot(data=shuff_slopes, aes(x = r2)) +
    coord_cartesian(xlim = c(0,1)) +
    geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
    xlab(expression(R^2)) +
    ylab("Proportion") +
    scale_y_continuous(breaks=c(0.00, 0.8)) +
    theme_classic() 
p_r2_shuffled


plot_grid(p_r2_real, p_r2_shuffled, ncol=1, align='v')
```



### Subfigs: slope comparison

```{r}
p_slope_comparison <- ggplot() + 
    geom_jitter(data=continuous,aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)) * sr_factor_outbound, y = as.numeric(unlist(asr_b_h_rewarded_fit_slope)) * sr_factor_homebound, color=factor(unlist(lm_group_b)))) +
    geom_jitter(data=reset,aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)) * sr_factor_outbound, y = as.numeric(unlist(asr_b_h_rewarded_fit_slope)) * sr_factor_homebound, color=factor(unlist(lm_group_b))), shape=1) +
    xlab("Outbound slope") +
    ylab("Homebound slope") +
    theme_classic() +
    scale_color_manual(values=c("violetred2", "chartreuse3")) +
    theme(legend.position="none",  legend.title = element_blank())

p_slope_comparison 
```


### Subfigs: heatmap

```{r}
wide_DF <- concat_firing_start %>% spread(Position, Rates)

colnames(wide_DF) <- c("new_cluster_id", rep(TRACK_OUTBOUND_START:TRACK_OUTBOUND_END, times=1))
rownames(wide_DF) <- paste("neuron", 1:max(start_ramps$new_cluster_id), sep="_")

name <- "new_cluster_id"
wide_DF <- wide_DF %>% select(-one_of(name))

mydf <- data.frame(row.names = paste("neuron", 1:max(start_ramps$new_cluster_id), sep="_"), catagory = lm_result, region = brain_region, ramp_score=ramp_result)

mydf <- data.frame(row.names = paste("neuron", 1:max(start_ramps$new_cluster_id), sep="_"), catagory = lm_result)

rownames(wide_DF) <- paste("neuron", 1:max(start_ramps$new_cluster_id), sep="_")
# change the color of annotation to what you want: (eg: "navy", "darkgreen")
Var1        <- c("violetred2", "black", "chartreuse3")
names(Var1) <- c("Negative", "Unclassified", "Positive")

Var2        <- c("springgreen4", "deepskyblue1", "firebrick", "violetred2" )
names(Var2) <- c('XX', "UN", "V1", "PreS")

anno_col <- list(result = Var1, region = Var2, ramp_score = brewer.pal(11,"RdBu"))

mydf <- mydf %>% filter(result != 'NAs')
wide_DF <- wide_DF %>% rownames_to_column() %>%
  filter(rowname %in% rownames(mydf)) %>%
  select(-rowname)

rownames(wide_DF) <- rownames(mydf)

myheatmap<-pheatmap(wide_DF,cluster_cols = F, cluster_rows = F, annotation_row = mydf, show_rownames = F, show_colnames = F, annotation_colors=anno_col, 
                    legend = F,  annotation_legend = F, annotation_names_row = F)
myheatmap

p_heatmap <- myheatmap
```



### Figure arrangement

Note: the image from panel A (network schematic) needs to be added manually. 

I have tried multiple methods of including the svg/pdf/png automatically but they all make the image look horrible...

```{r, fig.height=7, fig.width=11}
library("ggplotify")

grid_layout <- "AAABB
                AAABB
                CFFGJ
                DFFHJ
                EFFIJ"

# This placeholder object looks stupid but it is needed to preserve the panel label font size. 
spacer = ggplot() + custom_theme + theme(line = element_blank())

t = theme()

left_head_element_size = 17
p_untrained <- p_untrained_behaviour + labs(title = 'Non-beaconed before training') + theme(plot.title = element_text(size=left_head_element_size))
p_trained <- p_trained_behaviour + labs(title = 'Non-beaconed after training') + theme(plot.title = element_text(size=left_head_element_size))
p_probe <- p_probe_behaviour + labs(title = 'Probe trials') + theme(plot.title = element_text(size=left_head_element_size))

custom_theme = theme(text = element_text(size=global_text_size))
global_margin <- theme(plot.margin=unit(c(0.6, 0.6, 0.6, 0.6), units='cm'))
p <- spacer +  
  (p_training + global_margin) + 
  (p_untrained + global_margin) + 
  (p_trained + global_margin) + 
  (p_probe + global_margin) +
  (p_activations + global_margin) +
  (p_r2_real + custom_theme + global_margin) +
  (p_r2_shuffled + custom_theme + global_margin) +
  (p_slope_comparison + custom_theme + global_margin) +
  (as.ggplot(p_heatmap) + custom_theme + global_margin) +
  plot_layout(design = grid_layout) + plot_annotation(tag_levels = 'A') 

p


ggsave('plots/Figure6.png', p, height = 14, width = 19)
```



















